A fast and Low-Overhead Technique to Secure Programs Against Integer Overflows

### 2012-09-04 doc/Manuscript/CGO/paper.tex
Changing the title and inserting a number in the abstract

\title{Combining Static and Dynamic Analyses to Secure Programs against
Integer Overflows}
%\subtitle{A case study of the Dinamica EGO toolkit}

@@

\begin{abstract}
The integer primitive type has upper and lower bounds in many programming
languages, including C, C++ and Java.
This limitation might lead programs that manipulate large integer numbers to
produce unexpected results due to overflows.
There exists a plethora of works that instrument programs to track the occurrence
of these overflows.
In this paper we present an algorithm that relies on static range analysis to
eliminate this instrumentation whenever possible.
We present a novel live range splitting strategy that refine the precision of
our range analysis.
We have used this algorithm to improve the quality of a dynamic instrumentation
library that we have implemented in LLVM.
This framework has been used to detect overflows in hundreds of C/C++ programs.
As a testimony of its effectiveness, our range analysis has been able to speedup
the SPEC CPU 2006 instrumented programs by XX\%.
\end{abstract}

>>>>

\title{A fast and Low-Overhead Technique to Secure Programs Against
Integer Overflows}
%\title{Combining Static and Dynamic Analyses to Secure Programs against
%Integer Overflows}
%\subtitle{A case study of the Dinamica EGO toolkit}

@@

\begin{abstract}
The integer primitive type has upper and lower bounds in many programming
languages, including C, C++ and Java.
This limitation might lead programs that manipulate large integer numbers to
produce unexpected results due to overflows.
There exists a plethora of works that instrument programs to track the occurrence
of these overflows.
In this paper we present an algorithm that relies on static range analysis to
eliminate this instrumentation whenever possible.
We present a novel live range splitting strategy that refine the precision of
our range analysis.
We have used this algorithm to improve the quality of a dynamic instrumentation
library that we have implemented in LLVM.
This framework has been used to detect overflows in hundreds of C/C++ programs.
As a testimony of its effectiveness, our range analysis has been able to eliminate
19\% of all the overflow checks necessary to secure the C programs in the
SPEC CPU 2006 benchmark suite.
\end{abstract}
